\problemname{Expeditious Cubing}
\illustration{0.32}{rubik}{The classic Rubik's cube.\\
\href{https://commons.wikimedia.org/wiki/File:Rubiks_cube_by_keqs.jpg}{Picture} by Keqs on Wikimedia Commons, cc-by sa}%
Your friend Claire has dragged you along to a speedcubing event that
is happening in Eindhoven. These events are all about solving the
Rubik's cube and similar twisty puzzles as quickly as possible.
The attendants of the event can enter into various competitions based
on the type and size of the puzzle, and there are even special
competitions where the puzzles need to be solved one-handed or
blindfolded.

Claire is competing in the most popular competition: speedsolving the
$3\times3\times3$ Rubik's cube, pictured on the right. Each contestant
needs to solve the cube five times, each time with a different random
scramble. After all solves are completed, the best and the worst times
are discarded and the final score is the average of the remaining
three times. The contestant with the smallest final score wins.
% Claire explains that this rule ensures that the competition is
% not decided by a single lucky solve, for instance the current world
% record time for a single solve is 3.47 seconds, while the world
% record average is ``only'' a time of 5.69 seconds.

Claire has done well in the competition so far and is among the
contenders for the overall victory. All the other contestants have
already finished their five solves, but Claire has one solve remaining.
By looking at the final scores of the other contestants, she has deduced her
own target final score. As long as her final score is less than or equal to
this target score, she will be declared the overall winner.
Is it possible for her to win the competition, and if so, what is the
worst time she can have on her last solve in order to do so?

\section*{Input}

The input consists of:

\begin{itemize}
  \item One line with four real numbers $t_1$, $t_2$, $t_3$ and $t_4$, the times
    Claire got on her first four solves.
  \item One line with a real number $t$, Claire's target final score, the worst
      final score she can have in order to be declared the overall winner.
\end{itemize}

Each number is between $1$ and $20$, inclusive, and is given
with exactly two decimal places.

\section*{Output}

If it is not possible for Claire to win the event, output
``\texttt{impossible}''. If she will win regardless of the time she gets
on her last solve, output ``\texttt{infinite}''. Otherwise, output the
worst time she can have on her last solve in order to be declared the
overall winner. Output the number to \emph{exactly} two decimal places.
