\problemname{Game of Throwns}
Daenerys frequently invents games to help teach her second grade Computer
Science class about various aspects of the discipline. For this week's lesson
she has the children form a circle and (carefully) throw around a petrified
dragon egg.

The $n$ children are numbered from $0$ to $n - 1$ (it is a Computer Science class
after all) clockwise around the circle. Child $0$ always starts with the egg.
Daenerys will call out one of two things:
\begin{enumerate}
\item a number $t$, indicating that the egg is to be thrown to the child who is
$t$ positions clockwise from the current egg holder, wrapping around if
necessary.  If $t$ is negative, then the throw is to the counter-clockwise
direction.
\item the phrase {\tt undo $m$}, indicating that the last $m$ throws should be
undone.  Note that {\tt undo} commands never undo other {\tt undo} commands;
they just undo commands described in item $1$ above.
\end{enumerate}
For example, if there are $5$ children, and the teacher calls out the four throw
commands {\tt 8 -2 3 undo 2}, the throws will start from child $0$ to child $3$,
then from child $3$ to child $1$, then from child $1$ to child $4$. After this, the
{\tt undo 2} instructions will result in the egg being thrown back from child $4$
to child $1$ and then from child $1$ back to child $3$. If Daenerys calls out $0$ (or
$n, -n, 2n, -2n$, etc.) then the child with the egg simply throws it straight up
in the air and (carefully) catches it again.

Daenerys would like a little program that determines where the egg should end up
if her commands are executed correctly.  Don't ask what happens to the children
if this isn't the case.

\section*{Input}
Input consists of two lines. The first line contains two positive integers $n$
$k$ ($1\leq n \leq 30$, $1 \leq k \leq 100$) indicating the number of students
and how many throw commands Daenerys calls out, respectively. The following line
contains the $k$ throw commands. Each command is either an integer $p$
($-10\,000 \leq p \leq 10\,000$) indicating how many positions to throw the egg
clockwise or {\tt undo }$m$ ($m \geq 1$) indicating that the last $m$ throws
should be undone.  Daenerys never has the kids undo beyond the start of the
game.

\section*{Output}
Display the number of the child with the egg at the end of the game.
