\problemname{Tables}

HTML uses a simple tag format for table layout.  You are to create
ASCII-art tables based on a simplified notation.

Logically, a table can be considered an $m$ by $n$ grid, each with a
2-character wide by 1-character high cell, for example a $2 \times 3$ grid
would be as follows:
\begin{verbatim}
                               -- -- -- 
                              |11|12|13|
                               -- -- -- 
                              |21|22|23|
                               -- -- -- 
\end{verbatim}
The output consists of $2m+1$ rows, each having $3n+1$ characters
(including leading and trailing spaces in odd-numbered rows).

But some tables are not strictly grid-based, because the values for
certain cells can span multiple rows and/or columns.  Here is the
layout if cell 11 has a row span of 2 and cell 22 has a column span of
2:
\begin{verbatim}
                               -- -- -- 
                              |11|12|13|
                                  -- -- 
                              |  |22   |
                               -- -- --  
\end{verbatim}
You are to create these ASCII-art tables given $m$, and the row span
and column span values.  % given in left-to-right and top-to-bottom order.

\section*{Input}
The input consists of multiple test cases.
The first line of each test case contains one
integer $m$, the number of rows.
Then, $m$ lines follow, describing the row and column
spans in the layout.  Each of the next $m$ lines gives the span information
for a row. The span information is given only for the upper
left cell in the span.  If $N$ row spans and column spans need to be
specified for a given row, these would be specified as:
\[
N \  \texttt{RS}_1\  \texttt{CS}_1\  \ldots\ \texttt{RS}_N\ \texttt{CS}_N
\]
%\begin{verbatim}
%N RS(1) CS(1) ... RS(N) CS(N)
%\end{verbatim}
where the values $\texttt{RS}_k$ and $\texttt{CS}_k$ are between 1 and 9, and specify how
many rows and columns the next cell needing information in this row
needs to occupy.  Previous row spans or column spans may imply that
fewer cells than the total number of columns need to be specified
for a particular row.

%\newpage
You may assume that the input is valid:
\begin{itemize}
\item the number of rows and columns are between 1 and 9;
\item every row will have the same number of columns;
\item there are no overlapping spans of cells;
\item every cell is contained in some span of cells.
\end{itemize}

There are at most $100$ test cases and the end of input is indicated by $m
= 0$. 

\section*{Output}

For each case, display the ASCII-art table, with the row-column index
displayed in the top left corner of every span of cells. Display a blank
line after every case.
