\problemname{Social Advertising}

%\setlength{\columnsep}{15pt}

You have decided to start up a new social networking company.  Other
existing popular social networks already have billions of users, so
the only way to compete with them is to include novel features no
other networks have.

Your company has decided to market to advertisers a cheaper way to
charge for advertisements (ads).  The advertiser chooses which users'
``wall'' the ads would appear on, and only those ads are charged.
When an ad is posted on a user's wall, all of his/her friends (and of
course the user himself/herself) will see the ad.  In this way, an
advertiser only has to pay for a small number of ads to reach many
more users.

You would like to post ads to a particular group of users
with the minimum cost.  You already have the ``friends list'' of each
of these users, and you want to determine the smallest number of ads
you have to post in order to reach every user in this group.  In this
social network, if $A$ is a friend of $B$, then $B$ is also a friend
of $A$ for any two users $A$ and $B$.

\section*{Input}

The input consists of multiple test cases. The first line of input 
is a single integer, not more than $10$, indicating the number
of test cases to follow.  
Each case starts with a line containing an integer
$n$ ($1 \leq n \leq 20$) indicating the number of users in the group.
For the next $n$ lines, the $i$th line contains the friend list of
user $i$ (users are labelled $1, \ldots, n$).  Each line starts with
an integer $d$ ($0 \leq d < n)$ followed by $d$ labels of the friends.
No user is a friend of himself/herself.


\section*{Output}

For each case, display on a line the minimum number of ads needed to be
placed in order for them to reach the entire group of users.
