\problemname{Institute of Advanced Category Manipulation}

A certain magazine annually ranks universities across the country in
various categories, as a service for readers who may be deciding
which university to attend.  Each university is given three scores
$R$, $T$, and $S$ (integers from 0 to 100) for its research, teaching,
and community service, respectively. These scores are then interpreted
somehow and the top universities in a number of categories are named.
There are many categories to compete in (research university,
undergraduate university, small university, etc.).  Sometimes these
categories appear to be invented just to make a particular university
a ``top university'' (e.g. top university in rural area with
population 30,000 to 45,000).

The Institute of Advanced Category Manipulation (ACM) is not pleased
with its ranking, because it is not a top university in any
category.  The public relations department of ACM has decided that it
can invent its own category of universities, and rank each university
based on a linear combination of the three scores. The combined score
$U$ for each university is calculated by the formula:
\[ U = aR + bT + cS \] 
where $a$, $b$, $c$ are constant real numbers. To make sure that
the readers do not notice the scores suddenly getting too large or too
small, it is required that $a^2 + b^2 + c^2 = 1$. Since some of the
scores for ACM are low compared to its peers, they will even allow any
of $a$, $b$, and $c$ to be negative. A university is considered a top
university in the new category if its combined score is greater than
or equal to the combined scores of each of the other universities.
Each category is defined by the constants $(a,b,c)$ satisfying the
constraints given above.

This idea is quickly catching on among university administrators. For
example, the Research University of Ivory Towers has decided to use
$(a,b,c) = (0.57735, -0.57735, -0.57735)$.  Even with this
manipulation, some universities cannot be considered top universities.
In the second case of the sample input below, The University of
Mediocrity has a score of $R = T = S = 50$.  It cannot be considered a top
university among the given universities regardless of how it
manipulates the categories.

In this problem, you will be given the research, teaching, and
community service scores of some universities.  Your task is to
determine which of these universities can be considered a top
university.

\section*{Input}

The input consists of multiple test cases. The first line of input 
is a single integer, not more than $10$, indicating the number
of test cases to follow.  
The first line of each case is a positive integer
$n$ ($1 \leq n \leq 50$) specifying the number of universities to be
considered.  The following $n$ lines each contains three integers
specifying the research, teaching, and community service scores.  


\section*{Output}

For each case, display on a single line a string consisting of $n$
characters.  The $i$th character is \verb|T| if the $i$th university
given in the input can be considered a top university and \verb|F|
otherwise.
